A lottery model of density-dependent selection

### 2017-10-25 manuscript.tex
latest

MacArthur famously distinguished between ``$r$-selection'' for faster growth at low population density, and ``$K$-selection'' for the ability to keep growing at higher densities \citep{macarthur_1962,macarthur_1967}. While the $r$/$K$ scheme is primarily known for its seminal role in the study of life-history evolution \citep{pianka_1970,boyce_1984,charlesworth_1994,reznick_2002}, it
also initiated a sizeable literature on density-dependent selection. This literature is remarkable in that it contains some of earliest models of the interplay between ecology and evolution \citep{roughgarden_1979,travis_2013},

Identifying selection at high densities with ``$K$-selection'' is a compelling oversimplification. Starting from a very general description of density-regulated population growth
\begin{equation}
\frac{d n_1}{d t}=f_1(n_1,n_2)\qquad\frac{d n_2}{d t}=f_2(n_1,n_2)
\end{equation}

``population genetics of crowded populations where fitness is $K$''.

>>>>

MacArthur famously distinguished between ``$r$-selection'' for faster growth at low population density, and ``$K$-selection'' for the ability to keep growing at higher densities \citep{macarthur_1962,macarthur_1967}. While the $r$/$K$ scheme is primarily known for its seminal role in the study of life-history evolution \citep{pianka_1970,boyce_1984,charlesworth_1994,reznick_2002}, it
also initiated a sizeable literature on density-dependent selection. This literature is remarkable for containing some of earliest models of the interplay between ecology and evolution \citep{roughgarden_1979,travis_2013}.

In MacArthur's view, selection at high densities is ``$K$-selection'', such that in ``crowded populations ... fitness is $K$''. MacArthur's argument is based on general equations for density-regulated population growth
\begin{equation}
\frac{d n_1}{d t}=f_1(n_1,n_2)\qquad\frac{d n_2}{d t}=f_2(n_1,n_2),
\end{equation}
where, by definition, each
